### 2024-03-15 ms.qmd
Updates

Behavioural flexibility describes the ability of individuals to adjust behaviour adaptively in response to internal or external changes in the environment [@brown2010behavioral]. It comprises a suite of behavioural aspects like problem-solving, innovation, or alterations in one behaviour in favour of another [@brown2010behavioral]; all cognitive abilities predicted to be crucial for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can]. Species with greater behavioural flexibility are expected to be more likely to survive and establish in new habitats because behaving flexibly enhances their capacity to exploit new resources and face new challenges [@wright2010behavioral; @chapple2012can; @szabo2020can]. For instance, in closely related bird species successful invaders show a higher frequency of foraging innovations [@sol2000behavioural]. According to the 'adaptive flexibility hypothesis', behavioural flexibility is most relevant during introduction, establishment, and spread of an invasive population [@wright2010behavioral; @chapple2012can; @szabo2020can]. In mammals, birds, reptiles and amphibians, relative brain size has been shown to be a good predictor of behavioural flexibility and invasive success [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011]. However, the brain is also sensitive to environmental changes during the early stages of development [@zhu_prenatal_2004] creating uncertainty about how environmental insults faced by early invaders might impact behavioural flexibility and thus the probability of invasion success.    

>>>>

Behavioural flexibility describes the ability of individuals to adjust behaviour adaptively in response to internal or external changes in the environment [@brown2010behavioral]. It comprises a suite of behavioural aspects like problem-solving and innovation [@brown2010behavioral], that are predicted to be crucial for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can]. Species with greater behavioural flexibility are expected to be more likely to survive and establish in new habitats because behaving flexibly enhances their capacity to exploit new resources and face new challenges [@wright2010behavioral; @chapple2012can; @szabo2020can]. For instance, in closely related bird species successful invaders show a higher frequency of foraging innovations [@sol2000behavioural]. According to the 'adaptive flexibility hypothesis', behavioural flexibility is most relevant during introduction, establishment, and spread of an invasive population [@wright2010behavioral; @chapple2012can; @szabo2020can]. In mammals, birds, reptiles and amphibians, relative brain size has been shown to be a good predictor of behavioural flexibility and invasive success [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011]. However, the brain is also sensitive to environmental changes during the early stages of development [@zhu_prenatal_2004] creating uncertainty about how environmental insults faced by early invaders might impact behavioural flexibility and thus the probability of invasion success.    
